\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
wordsmith for style and made a sentence less awkward

\subsection{Testing Pipeline} 
We began by performing a cognitive walkthrough~\cite{wharton1994cognitive,cognitive-walkthrough} to inspect the interface to anticipate potential problems and formally assess its pros and cons.
A cognitive walkthrough is a formal method of inspection performed by researchers without any user involvement.
We then conducted qualitative and quantitative usability tests.
We believe both methods were necessary for a complete usability evaluation.
Qualitative testing illuminates {\it why or how} the software is or is not usable, while quantitative testing measures {\it to what extent}.
We used our observations from the qualitative study to design interface changes that would address common issues that participants encountered.
We used our quantitative testing setup to measure the usability of our proposed changes, as compared to the original interface.

>>>>

\subsection{Testing Pipeline} 
We began by performing a cognitive walkthrough~\cite{wharton1994cognitive,cognitive-walkthrough} to inspect the interface to anticipate potential problems and formally assess its pros and cons.
A cognitive walkthrough is a formal method of inspection performed by researchers without any user involvement.
We then conducted qualitative and quantitative usability tests.
We believe both methods were necessary for a complete usability evaluation.
Qualitative testing illuminates {\it why or how} the software is or is not usable, while quantitative testing measures {\it to what extent}.
We used our qualitative study observations to design interface changes that would address encountered issues.
We used quantitative testing to measure the impact of our proposed changes, as compared to the original interface.
